%
% Copyright © 2013 Peeter Joot.  All Rights Reserved.
% Licenced as described in the file LICENSE under the root directory of this GIT repository.
%
%\part{Readings}
%   \include{readings}
%\part{Approximate methods and pertubation}
   \mychapter{Approximate methods.}
      \input{approx/qmTwoL2.tex}
   \mychapter{Perturbation methods.}
      \input{approx/qmTwoL3.tex}
      \section{Problems.}
         %\subsection{Problem set 1}
         \input{problems/phy456ps1.tex}
         %\subsection{Helium atom ground state energy estimation.}
         \input{problems/variationalHelium.tex}
         %\subsection{Curious problem using the variational method to find the ground state energy of the Harmonic oscillator.}
         \input{problems/variationHarmonicOscillator.tex}
   \mychapter{Time independent perturbation.}
      \input{approx/qmTwoL3TimeIndepPert.tex}
      \input{approx/qmTwoL4.tex}
      \input{approx/qmTwoL5.tex}
      \section{Examples.}
         \input{approx/qmTwoR3Stark.tex}
   \mychapter{Time dependent perturbation.}
      \input{approx/qmTwoL5Dynamics.tex}
      \input{approx/qmTwoL6.tex}
      \input{approx/qmTwoL7.tex}
      \input{approx/qmTwoL8.tex}
      \input{approx/qmTwoL9.tex}
      \section{Examples.}
         \input{approx/qmTwoR3Adiabatic.tex}
   \mychapter{Fermi's golden rule.}
%      \input{approx/qmTwoL9FermiGoldenRule.tex}
      \input{approx/qmTwoL10.tex}
      \section{Problems.}
      %\mychapter{Sinc squared integral.}
         \input{problems/sincIntegral.tex}
   \mychapter{WKB Method.}
      \input{approx/qmTwoL12.tex}
      \section{Examples.}
         \input{approx/qmTwoR3.tex}
%\part{Spin, angular momentum, and two particle systems}
   \mychapter{Composite systems.}
      \input{spin/qmTwoL1.tex}
   \mychapter{Spin and Spinors.}
      \input{spin/qmTwoL11.tex}
      \input{spin/qmTwoL13.tex}
   %\mychapter{Representation of two state kets and Pauli spin matrices.}
   \mychapter{Two state kets and Pauli matrices.}
      \input{spin/qmTwoL14.tex}
   \mychapter{Rotation operator in spin space.}
      \input{spin/qmTwoL15.tex}
   %\mychapter{Hydrogen atom with spin}
      \input{spin/qmTwoL16.tex}
   \mychapter{Two spins, angular momentum, and Clebsch-Gordon.}
      \input{spin/qmTwoL16TwoSpin.tex}
      \input{spin/qmTwoL17.tex}
%   \mychapter{The Clebsch-Gordon convention for the basis elements of summed generalized angular momentum}
      \input{spin/qmTwoL18.tex}
   \mychapter{Rotations of operators and spherical tensors.}
      \input{spin/qmTwoL19.tex}
   %\mychapter{Spherical tensors}
      \input{spin/qmTwoL20.tex}
%\part{Scattering theory}
   \mychapter{Scattering theory.}
      \input{scattering/qmTwoL21.tex}
      \input{scattering/qmTwoL22.tex}
   \mychapter{3D Scattering.}
      \input{scattering/qmTwoL23.tex}
      \input{scattering/qmTwoL24.tex}
   \mychapter{Born approximation.}
      \input{scattering/qmTwoL25.tex}
