%
% Copyright © 2012 Peeter Joot.  All Rights Reserved.
% Licenced as described in the file LICENSE under the root directory of this GIT repository.
%

%
%
%\chapter{Preface}
% this suppresses an explicit chapter number for the preface.
\chapter*{Preface}%\normalsize
  \thispagestyle{empty}

These are my personal lecture notes for the Fall 2011, University of Toronto Quantum mechanics II course (PHY456H1F), taught by Prof.\ John E Sipe.

The official description of this course was:

Quantum dynamics in Heisenberg and Schrodinger Pictures; WKB approximation; Variational Method; Time-Independent Perturbation Theory; Spin; Addition of Angular Momentum; Time-Dependent Perturbation Theory; Scattering.

This document contains a few things
\begin{itemize}
\item My lecture notes.
\item Notes from reading of the text \citep{desai2009quantum}.  This may include observations, notes on what seem like errors, and some solved problems.
\item Different ways of tackling some of the assigned problems than the solution sets.
\item Some personal notes exploring details that were not clear to me from the lectures.
\item Some worked problems.
\end{itemize}

There were three main themes in this course, my notes for which can be found in
\begin{itemize}
   \item Approximate methods and perturbation: \cref{chap:qmTwoL2}-\cref{chap:qmTwoL12},
   \item Spin, angular momentum, and two particle systems: \cref{chap:qmTwoL1}-\cref{chap:qmTwoL19},
   \item Scattering theory: \cref{chap:qmTwoL21}-\cref{chap:qmTwoL25},
\end{itemize}

Unlike some of my other course notes compilations, this one is short and contains few worked problems.  It appears that I did most of my problem sets on paper and subsequently lost my solutions.  There are also some major defects in these notes:
\begin{itemize}
   \item There are plenty of places where things weren't clear, and there are still comments to followup on those issues to understand them.
   \item There is redundant content, from back to back lectures on materials that included review of the previous lecture notes.
   \item A lot of the stuff in the appendix (mostly personal notes and musings) should be merged into the appropriate lecture note chapters.  Some work along those lines has been started, but that work was very preliminary.
   \item I reworked some ideas from the original lecture notes to make sense of them (in particular, adiabatic approximation theory), but then didn't go back and consolidate all the different notes for the topic into a single coherent unit.
\iftoggle{print-version}{}
{
   \item There were Mathematica notebooks for some of the topics with issues that I never did figure out.
}
   \item Lots of typos, bad spelling, and horrendous grammar.
   \item The indexing is very spotty.
\end{itemize}
Hopefully, despite these and other defects, these notes may be of some value to other students of Quantum Mechanics.

I'd like to thank Professor Sipe for teaching this course.  I learned a lot and it provided a great foundation for additional study.

Peeter Joot  \quad peeterjoot@pm.me
